\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-12 Manuscript/Manuscript.tex
added citation in Poisson section

A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}. This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data. The Poisson distribution's p.m.f is:
\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]

>>>>

A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}. This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}. The Poisson distribution's p.m.f is:
\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]
